lifespan_eda

### 2023-12-12 eda/lifespan_eda.Rmd

ggarrange(ven_raw, ven_gam, ven_gamlss, ven_raw.imp, ven_gam.imp, ven_gamlss.imp, common.legend = TRUE)
```

>>>>

neg_ventricle_plots <- ggarrange(ven_raw, ven_gam, ven_gamlss, ven_raw.imp, ven_gam.imp, ven_gamlss.imp, common.legend = TRUE)
#ggsave(paste0(base_path, "figs/lifespan_ventricle_neg.jpg"), plot=neg_ventricle_plots)
```
